data-cleaning

### 2022-04-27 scripts/data-cleaning.Rmd
cleaning up code

  df_list[[i]] <- df_year
}
# 
# filename <- "../inputs/data/bus/ttc-bus-delay-data-2014.xlsx"
# sheetnames <- getSheetNames(filename)
# for(i in 1:length(sheetnames)) {
#   print(sheetnames[i])
#   df <- read(excel)
# }
# bus_2014 <- read_excel("../inputs/data/bus/ttc-bus-delay-data-2014.xlsx", 1)
# 
# df <- data.table(bus_2014)
# head(df)
```

@@

# delay times are slightly increasing actually - this is surprising
# segment growth by routes?
```
#### Saving to RData
```{r}
df_all_years <- copy(rbindlist(df_list, fill = TRUE))
# head(df_all_years)

@@

```{r}
# drop incident_id column - only present in 1 month (5k out of 517k total rows)
df_all_years[, incident_id := NULL]

@@

# rough work below
```{r}
df_list[[1]][, month(`Report Date`)]

>>>>

  df_list[[i]] <- df_year
}

# EXPLORATORY CLEANING - DO NOT NEED TO RUN
Skip ahead to **FINAL CLEANING CHUNK**

@@

# delay times are slightly increasing actually - this is surprising
# segment growth by routes?
```
```{r}
df_all_years <- copy(rbindlist(df_list, fill = TRUE))
# head(df_all_years)

@@

# FINAL CLEANING CHUNK
```{r}
# drop incident_id column - only present in 1 month (5k out of 517k total rows)
df_all_years[, incident_id := NULL]

@@

# rough work below - no need to run
```{r}
df_list[[1]][, month(`Report Date`)]
